Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}

### 2020-03-28 paper.tex
Modify "Algorithm" Section
Add "Flowchart" Subsection

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% \makeatletter
% % \newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
% %     \def\@fs@pre{}%
% %     \def\@fs@post{}%
% %     \def\@fs@mid{\kern3pt}%
% %     \let\@fs@iftopcapt\iftrue}
% \makeatother
% \floatstyle{norules}
% \restylefloat{algorithm}

@@

\subsection{Proposed Algorithm}

\begin{algorithm}[H]
    \caption{Enhanced Multilevel FeedBack Queue Scheduling Algorithm}
    \begin{algorithmic}[1]
    \Procedure {EMLFQ}{Number of processes $n$, priority of each process $\alpha_{i}$, burst time of each process $\beta_{i}$}
    % Return  Average waiting time, throughput
    \Statex Declaration and Initialisation:
    \State Queue $Q_{i}$ where $i \in \{0, 1, 2, 3, 4\}$, waiting time $\omega_{i} = 0$ of $P_{i}$, quantum time $\Gamma$, quantum time index $\gamma$
        \For {$i = 0$ to $n$}
            \State \textbf{Assign} $P_{i}$ to $Q_{\alpha_{i}}$
        \EndFor
    \Statex Loop Process:
        \State $i = 0$
        \While {$Q_{i}$ is NOT empty}
            % Aging Processes
            \For{$j = i + 1$ to $5$}
                \If{$1-\omega_{\theta}/\beta_{\theta} < 0.95$ for $\theta \in Q_{j}$}
                    \State \textbf{Promote} $P_{\theta}$ to the current queue $Q_{i}$
                \EndIf
            \EndFor

            % Calculating the quantum time value
            \Statex Calculating the quantum time value:
            \State $ascending\_sort(\beta_{Q_{i}})$
            \State $\gamma = Q_{i}.size()/2 + i$
            \State $\Gamma = \beta_{\gamma}$ where $\beta_{\gamma} \in Q_{i}$
            % Assigning the quantum value to each process in the queue
            \Statex Assigning the Quantum Value to each Process:
            \For{$P_{j}$ in $Q_{i}$}
                \State $\beta_{j} = \beta_{j} - \Gamma$
                \If{$\beta_{j} <= 0$}
                    \State \textbf{Remove} $P_{j}$ from $Q_{i}$
                \ElsIf {$i < 4$}
                    \State \textbf{Downgrade} $P_{j}$ to $Q_{i+1}$
                \EndIf
            \EndFor
            % Increment waiting time
            \Statex Increment Waiting Time:
            \For{$j = 0$ to $n$}
                \State $\omega_{j} = \omega_{j} + 1$
            \EndFor
            \Statex Increment Queue Index
            \If{$i < 4$}
                \State $i = i + 1$
            \EndIf
        \EndWhile
     \EndProcedure
    \end{algorithmic}
\end{algorithm}

\subsection{Flowchart of the Proposed Algorithm}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\makeatletter
\newcommand\fs@norules{\def\@fs@cfont{\bfseries}\let\@fs@capt\floatc@ruled
    \def\@fs@pre{}%
    \def\@fs@post{}%
    \def\@fs@mid{\kern3pt}%
    \let\@fs@iftopcapt\iftrue}
\makeatother

\tikzstyle{startstop} = [ellipse,minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{decision} = [diamond, minimum width=2cm, minimum height=1cm, text centered, draw=black, fill=white]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\subsection{Pseudocode Flowchart of the Proposed Approach}
\vspace{5mm}
\begin{tikzpicture}[node distance=2cm]

    \node (start) [startstop] {Start};
    \node (in1) [io, below of=start, text width = 2cm] {Read Processes Data};
    \node (pro1) [process, below of=in1, text width = 3cm] {Assign processes to their respective queue};
    \node (dec1) [decision, below of=pro1, text width = 2cm, yshift=-1cm] {All queues are empty};
    \node (end) [startstop, left of=dec1, xshift=-2cm] {End};
    \node (pro2) [process, below of=dec1, text width= 3cm, yshift = -1cm] {Iterate on non-empty queues $Q$};
    \node (dec2) [decision, below of=pro2, text width = 2cm, yshift=-1cm] {A process $P_{j}$ in $Q_{i+1}$ is boostable};
    \node (pro3) [process, left of=dec2, text width= 3cm, xshift= -2.2cm] {Promote $P_{j}$ to $Q_{i}$};
    \node (pro4) [process, below of=dec2, text width= 3cm, yshift=-1.2cm] {Calculate the quantum time value $\Gamma$ of $Q_{i}$};
    \node (pro5) [process, below of=pro4, text width= 3cm] {Assign $\Gamma$ to $Q_{i}$ processes};
    \node (pro6) [process, below of=pro5, text width= 3cm] {Downgrade incomplete processes to $Q_{i+1}\,:\,i+1 < 5$};
    \node (pro7) [process, below of=pro6, text width= 3cm] {Increment waiting time of $P_{j} \notin Q_{i}$};

    \draw [arrow] (start) -- (in1);
    \draw [arrow] (in1) -- (pro1);
    \draw [arrow] (pro1) -- (dec1);
    \draw [arrow] (dec1) -- node[anchor=west, above] {Yes} (end);
    \draw [arrow] (dec1) -- node[anchor=south, left] {No} (pro2);
    \draw [arrow] (pro2) -- (dec2);
    \draw [arrow] (dec2) -- node[anchor=west,above] {Yes} (pro3);
    \draw [arrow] (pro3.north) -- ++ (0,1.3) -- ++ (4.2,0);
    \draw [arrow] (dec2) -- node[anchor=south, left] {No} (pro4);
    \draw [arrow] (pro4) -- (pro5);
    \draw [arrow] (pro5) -- (pro6);
    \draw [arrow] (pro6) -- (pro7);
    \draw [arrow] (pro7.west) -- ++ (-4.5,0) -- ++(0,16.8) -- ++(6.1,0);

    \end{tikzpicture}

\subsection{Proposed Algorithm}
\floatstyle{norules}
\restylefloat{algorithm}
\begin{algorithm}[H]
    \caption{Enhanced Multilevel FeedBack Queue Scheduling Algorithm}
    \begin{algorithmic}[1]
    \Procedure {EMLFQ}{Number of processes $n$, priority of each process $\alpha_{i}$, burst time of each process $\beta_{i}$}
    % Return  Average waiting time, throughput
    \Statex Declaration and Initialisation:
    \State Queue $Q_{i}$ where $i \in \{0, 1, 2, 3, 4\}$, waiting time $\omega_{i} = 0$ of $P_{i}$, quantum time $\Gamma$, quantum time index $\gamma$
        \For {$i = 0$ to $n$}
            \State \textbf{Assign} $P_{i}$ to $Q_{\alpha_{i}}$
        \EndFor
    \Statex Loop Process:
        \State $i = 0$
        \While {$Q_{i}$ is NOT empty}
            % Aging Processes
            \For{$j = i + 1$ to $5$}
                \If{$1-\omega_{\theta}/\beta_{\theta} < 0.95$ for $\theta \in Q_{j}$}
                    \State \textbf{Promote} $P_{\theta}$ to the current queue $Q_{i}$
                \EndIf
            \EndFor

            % Calculating the quantum time value
            \Statex Calculating the quantum time value:
            \State $ascending\_sort(\beta_{Q_{i}})$
            \State $\gamma = Q_{i}.size()/2 + i$
            \State $\Gamma = \beta_{\gamma}$ where $\beta_{\gamma} \in Q_{i}$
            % Assigning the quantum value to each process in the queue
            \Statex Assigning the Quantum Value to each Process:
            \For{$P_{j}$ in $Q_{i}$}
                \State $\beta_{j} = \beta_{j} - \Gamma$
                \If{$\beta_{j} <= 0$}
                    \State \textbf{Remove} $P_{j}$ from $Q_{i}$
                \ElsIf {$i < 4$}
                    \State \textbf{Downgrade} $P_{j}$ to $Q_{i+1}$
                \EndIf
            \EndFor
            % Increment waiting time
            \Statex Increment Waiting Time:
            \For{$j = 0$ to $n$ \textbf{and} $P_{j} \notin Q_{i}$}
                \State $\omega_{j} = \omega_{j} + 1$
            \EndFor
            \Statex Increment Queue Index
            \If{$i < 4$}
                \State $i = i + 1$
            \EndIf
        \EndWhile
     \EndProcedure
    \end{algorithmic}
\end{algorithm}
